Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-22 Paper/gammaRays.tex
Fixed maximal energy from 1000000 to 300000
1000000 is not allowed in Fermi tools documentation

Now, with basic filtering done, we can read events data from \texttt{timed.fits}. This file, however, contains observations of a large area of the sky.
Before using the data obtained from it, we should perform a more elaborate filtering by location using the point spread function of Fermi LAT, which can be computed with \texttt{gtpsf}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtpsf.txt}} tool.
We use 41 energy bins from \unit[100]{MeV} to \unit[1]{TeV}, and 300 angular bins with maximal angle being $30\degree$.
We use \texttt{gtltcube}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtltcube.txt}} tool to compute livetime maps, which are \texttt{gtpsf} need.
Note, that we need PSFs for all Instrument Response Functions of Fermi, that is for all event classes (transient, source, clean and ultraclean) and conversion types (back and front).

@@

The exposure map can be computed with the \texttt{gtexpcube2}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtexpcube2.txt}} tool. We compute it with 40 energy bins from \unit[100]{MeV} to \unit[1]{TeV}.

@@

\begin{lstlisting}
gtpsf expcube=ltcube.fits outfile=psf_[IrfName].fits outtable=PSF irfs=[IrfName]
	ra=[RA] dec=[DEC] emin=100 emax=1000000 nenergies=41 thetamax=30 ntheta=300
\end{lstlisting}
\texttt{[RA]} and \texttt{[DEC]} here are the coordinates of the burst, and \texttt{[IrfName]} is the Instrument Response Function, which depends on photon's event class (transient, source, clean, or ultraclean) and conversion type (back or front). The list of IRF names can be obtained with the \texttt{gtirfs}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtirfs.txt}} tool. We need to compute PSFs for all of them.

\begin{lstlisting}
gtexpcube2 infile=ltcube.fits cmap=none outfile=expcube_[IrfName].fits irfs=[IrfName]
	nxpix=360 nypix=180 binsz=1 coordsys=CEL xref=0 yref=0 axisrot=0
	proj=CAR ebinalg=log emin=100 emax=1000000 enumbins=40
	ebinfile=NONE bincalc=EDGE ignorephi=no thmax=180 thmin=0 table=Exposure
\end{lstlisting}
Note, that R.A. coordinates in the \texttt{expcube} FITS files are indexed in reverse order and starting from 180. For example, $\texttt{ra[0]}=180$, $\texttt{ra[1]}=179$, and so on.

>>>>

Now, with basic filtering done, we can read events data from \texttt{timed.fits}. This file, however, contains observations of a large area of the sky.
Before using the data obtained from it, we should perform a more elaborate filtering by location using the point spread function of Fermi LAT, which can be computed with \texttt{gtpsf}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtpsf.txt}} tool.
We use 41 energy bins from \unit[100]{MeV} to \unit[300]{GeV}, and 300 angular bins with maximal angle being $30\degree$.
We use \texttt{gtltcube}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtltcube.txt}} tool to compute livetime maps, which are \texttt{gtpsf} need.
Note, that we need PSFs for all Instrument Response Functions of Fermi, that is for all event classes (transient, source, clean and ultraclean) and conversion types (back and front).

@@

The exposure map can be computed with the \texttt{gtexpcube2}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtexpcube2.txt}} tool. We compute it with 41 energy bins from \unit[100]{MeV} to \unit[300]{GeV}.

@@

\begin{lstlisting}
gtpsf expcube=ltcube.fits outfile=psf_[IrfName].fits outtable=PSF irfs=[IrfName]
	ra=[RA] dec=[DEC] emin=100 emax=300000 nenergies=41 thetamax=30 ntheta=300
\end{lstlisting}
\texttt{[RA]} and \texttt{[DEC]} here are the coordinates of the burst, and \texttt{[IrfName]} is the Instrument Response Function, which depends on photon's event class (transient, source, clean, or ultraclean) and conversion type (back or front). The list of IRF names can be obtained with the \texttt{gtirfs}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtirfs.txt}} tool. We need to compute PSFs for all of them.

\begin{lstlisting}
gtexpcube2 infile=ltcube.fits cmap=none outfile=expcube_[IrfName].fits irfs=[IrfName]
	nxpix=360 nypix=180 binsz=1 coordsys=CEL xref=0 yref=0 axisrot=0
	proj=CAR ebinalg=log emin=100 emax=300000 enumbins=40
	ebinfile=NONE bincalc=EDGE ignorephi=no thmax=180 thmin=0 table=Exposure
\end{lstlisting}
Note, that R.A. coordinates in the \texttt{expcube} FITS files are indexed in reverse order and starting from 180. For example, $\texttt{ra[0]}=180$, $\texttt{ra[1]}=179$, and so on.
